---
title: "Journal"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```
# Problem 1
Do simple math with numbers, addition, subtraction, multiplication, division

```{r}
1+2
2*5
5/3
(1+6+4)/5

```
# Problem 2
Put numbers into variables, do simple math on the variables
```{r}
a<-1
b<-2
a+b
d<-c(1,2,3)
e<-c(5,6,7)
d+e
d*e
d/e
```
# Problem 3
Write code that will place the numbers 1 to 100 separately into a variable using for loop. Then, again using the seq function.
```{r}
for (number in 1:100){
  cat(number, "\n")
}
```
# Problem 4
Find the sum of all the integer numbers from 1 to 100.
```{r}
sum(1:100)
```
# Problem 5
Using a for loop to sum 1 through 100
I'm having trouble with this one. I don't really understand what I'm doing
```{r}
# Sequence
seq <- c(1:100)

# Print loop
for (value in seq) {
    print(seq)
}

# A sum variable
sum(seq)
```
# Problem 6
List all of the prime numbers from 1 to 1000.
I found a code on the internet that works, though I don't understand what each part is doing.
```{r}
is.prime <- function(x) {
  x <- abs(as.integer(x))
  !grepl('^1?$|^(11+?)\\1+$', strrep('1', x))
}

(1:1000)[is.prime(1:1000)]
```

# Problem 7
Generate 100 random numbers
I'm not sure how to get runif to do whole numbers
```{r}
sample.int(100)

runif(100)
```
# Problem 8
Generate 100 random numbers within a specific range
Not sure how to get runif to do whole numbers
```{r}
sample(50:80,100, replace = TRUE)
runif(100,50,80)
```

```


