---
title: "R Instrinsics"
output: html_document
---
# **Built in R Functions**

I will be using this page to go through the different functions that are a part of r coding.

# Help Function
This function allows you to search different topics to get a description.
```{r}
help("save")
```
# Indexing vectors
The first allows you to make a vector and the following functions allows you to index that vector. 
```{r}
vector <- c(1,2,3,4,5,6,7,5,4,3,1,7,8,6,4)
vector[5]
vector[2:7]
vector[c(10,10,10,10,10,10,10,10,10,10)]
vector[c(2,8,9,5,4,2)]
vector[vector > 4]
vector[vector == 5]
vector[vector != 5]
vector[8] <- 3000
vector[1:2] <-c(10,15)
vector
```
# class()
This allows you to determine what type of variable you have.
```{r}
d = "Casey"
a = 2
class(d)
class (a)
```
# Variable Converting
```{r}
a <-c("1","2","3")
class(a)
b <- a
class(b)
as.numeric(b)
```
# List function
This function helps you create lists
```{r}
a <- "abcdefghijklmnop"
strsplit(a,split="")
b <- a
b <-strsplit(a,split="")
b[[1]][3]

class(b)

```

# Getting rid of a list
```{r}
a <-"qrstuvwxyz"
b <- unlist(strsplit(a,split=""))
class(a)
class(b)
```

# data frame
```{r}
first_names <- c("francis", "jean", "lou")
ages <- c(20,25,23)
grades <- c(99,70,84)
everybody <- data.frame(first_names, ages, grades)
print(everybody)

everybody$first_names
```


